Enrich the datasets with new columns.

### 2020-08-20 inst/analysis/enrich_dataset.Rmd
Add the number of calls of each deduplicated calls.

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.3/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.3/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

Let's remove the duplicate ones:

```{r}
eval_calls_base <- eval_calls_base %>% select(-eval_call_id, -starts_with("caller_stack")) %>% distinct()

eval_calls <- eval_calls_base %>% select(-eval_call_id) %>% distinct()
```

@@

```{r}
# We are doing some work once again! Parsing what was deparsed previously...
eval_calls <-  eval_calls %>% mutate(function_expr = if_else(expr_expression_type == "LANGSXP", map_chr(expr_expression, function_name), NA), function_expr_resolved = if_else(expr_resolved_type == "LANGSXP", map_chr(expr_resolved, function_name), NA))
```

@@

write_dst(eval_calls_base, paste0(params$data_dirpath, "base_calls.fst"))
```

>>>>

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.4/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.4/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

Let's remove the duplicate ones (but keep:

```{r}
eval_calls_base <- eval_calls_base %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_eval_calls") 
eval_calls <- eval_calls %>% count(across(c(-eval_call_id)), name = "nb_eval_calls")
```

@@

@@

write_fst(eval_calls_base, paste0(params$data_dirpath, "base_calls.fst"))
```
